Status and Best Practices for Reproducible Research In Plant Pathology

### 2018-01-10 inst/paper/Sparks_et_al-main_text.Rmd
Update main text with a point about proper archives

- Citation of methods, software, packages, etc.
- deposit and annotate biological materials
- provide full description for equipments, etc.

@@

### Repository
- Using GitHub for code (and small data?)
- Using Figshare or Zenodo vs a lab website (DOIs, other reasons)

>>>>

- Citation of methods, software, packages, etc.
- deposit and annotate biological materials
- provide full description for equipments, etc.
- rOpenSci Reproducible Research: http://ropensci.github.io/reproducibility-guide/sections/introduction/

@@

### Repository
- Using GitHub for code (and small data?)
- Using Figshare or Zenodo vs a lab website (DOIs, other reasons)
- Most ideal a library or other proper long-term data archival service
